% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Aaron B. Todd\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Contact} \\ jobs@aarontodd.name \\ (415) 847-0997 }

\address{{\bf Address} \\ 8 Haviland St. Apt B \\ Norwalk, CT 06854 }


\begin{resume} 
 
\section{Education}
B.A. in Computer Science, Grinnell College \hfill \textit{May 2011} \\
M.S. in Computer Science, Indiana University Bloomington \hfill \textit{May 2013}
\begin{itemize} \itemsep -2pt
\item Recieved as part of the PhD program, dropped out December 2013.
\item Research focus on programming language theory and parallelism.
\end{itemize}  
 

\section{Work Experience}

 {\bf Bridgewater Associates, Westport, CT} \hfill \textit{Jan 2014 - Present} \\
 Senior Software Developer
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item All work in Scala.
 \item Implemented features for economics research platform used by investment associates.
 \item Built optimization algorithms for trade generation pipeline in account management department.
 \item Designed and implemented domain specific language for algo developers to use.
 \item Mentored junior developers and instructed the team in functional programming concepts.
 \end{itemize}

 {\bf Mozilla, Mountain View, CA} \hfill \textit{Summer 2013} \\
 Research Engineering Intern
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Worked on implementation of green thread runtime with workstealing scheduler.
 \item Implemented directly in Rust.  
 \end{itemize}
  
\section{Academic Experience}

 {\bf PL Wonks} \hfill \textit{August 2013 - December 2013} \\
 Indiana University Bloomington \\
 Research Assistant
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Adviser Ryan Newton.
 \item Researched deterministic parallel programming working in the Haskell.
 \item Work on a deterministic parallel merge sort published at PLDI 2014.
 \end{itemize}


 {\bf Pervasive Technology Institute} \hfill \textit{August 2011 - May 2013} \\
 Indiana University Bloomington \\
 Research Assistant
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Adviser Beth Plale.
 \item Implemented REST API abstracting over compute resources in Scala and Akka for the HathiTrust Research Center.
 \end{itemize}
 
\section{Publications}

Kuper, L., \underline{Todd, A.}, Tobin-Hochstadt S., Newton, R.R. {\bf Taming the Parallel Effect Zoo, Extensible Deterministic Parallelism with LVish} \textit{PLDI '14} 

Kowalczyk, S. T., Sun, Y., Peng, Z., Plale, B., \underline{Todd, A.}, Auvil, L., Willis, C., Zeng, J., Pathirage, M., Liyanage, S., Ruan, G., Downie, J. S. {\bf Big Data at Scale for Digital Humanities: An Architecture for the HathiTrust Research Center} \textit{Big Data Management, Technologies, and Applications, Wen-Chen Hu and Naima Kaabouch (eds)} Book Chapter, IGI Global, 2013

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Languages:} & Scala, Scheme, SQL, Rust, C, Haskell \\
    \underline{Preferred Tools:} & Linux, Git, Emacs, i3wm, IntelliJ
   \end{tabular}

\end{resume} 
\end{document} 
